---
title: "Cross Validation"
output: github_document
---
```{r}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```


## Simulate Data

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

```

Look at data... it is non linear

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

## Cross validation -- by hand

Get training and testing datasets

```{r}
## sample 80 observations
train_df = sample_n(nonlin_df, size = 80)

## the remaining 20 goes into test dataset (observations in nonlin_df BUT not in training df)
test_df = anti_join(nonlin_df, train_df, by = "id")
```


## Build models using training dataset

```{r}
linear_model = lm(y ~ x, data = train_df)
#smooth model
smooth_mod = gam(y ~ s(x), data = train_df)
#very wiggly model
wiggle_mod = gam(y ~s(x, k = 30), sp = 10e-6, data = train_df)
```

Can I see what I just did 
"add_predictions" adds a column of fitted values 
```{r}
## too linear
train_df %>% 
  add_predictions(linear_model) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

## good (looks like it will do best at predictioj accuracy)
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")

## too wiggly
train_df %>% 
  add_predictions(wiggle_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Add predictions for multiple models at the same time 
```{r}
train_df %>% 
  gather_predictions(linear_model, smooth_mod, wiggle_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") +
  facet_grid(. ~model)
```

Look at prediction accuracy (calculate root mean squared error) (have to look at test dataset)

```{r}
## largest
rmse(linear_model, test_df)
## smallest (best)
rmse(smooth_mod, test_df)
## middle
rmse(wiggle_mod, test_df)
```


## Cross validation using `modelr` package

This package automates the process of generating a testing and training dataset
100 cross validation runs
Drawing mulitple samples from a dataset that already exists
100 different datasets that sample different stuff from the existing dataset
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

What is going on here...
We can covert any one of those samples into dataframes
```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()
```

I want list columns of straight dataframes, not resamples
```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Let's try to fit models and get RMSEs for them

Fit linear models for every element in the training column (100 dataframes)
Produces a list column with linear models
map_dbl gives it as a number rather than a list
```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~s(x, k = 30), sp = 10e-6, data = .x))
  ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

How do we know which model is the best?

Plotted the distribution over 100 different training sets for 3 different models
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


Commute averages of rmse
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

