---
title: "Linear Regression"
output: github_document
---
```{r}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Import Data 

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

## Fit a model
How price of rental is related to the stars and borough
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

let's look at the results

```{r, include = FALSE}
fit

summary(fit)

summary(fit)$coef

fitted.values(fit)
residuals(fit)

```

Let's look at the results better
```{r}
## get AIC and BIC and log likelihood (good when comparing models)
broom::glance(fit)

## structured as a dataframe 
broom::tidy(fit) %>% 
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable(digits = 2)
```


## Be in control of factors

Bronx is the reference group because of alphabetical order
What is we want the most common one (most number of air bnbs) to be the ref group
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

Look at plot again

```{r}
## Now borough (x axis) is in order of frequency of air bnb
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

Look at model again (different ref group - Manhattan is ref group)
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
broom::tidy(fit) ## betas are different
broom::glance(fit) ## these values are the same
```

